\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-24 paper.tex
Remove pictures and equation

\subsubsection{TangleID}
The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that does not require any third-party authority to verify an identity and its digital footprint. With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C. Posting DID documents on MAM makes TangleID a GDPR-Complianced system\cite{GDPR}. Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.

>>>>

\subsubsection{TangleID}
The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint. With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C. Posting DID documents on MAM makes TangleID a GDPR-Complianced system. Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.
